---
title: 'Reproducible Research: Peer Assessment 1'
author: "Alpatov"
date: '19 april 2018 ã '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading and preprocessing the data

Load the data and read data (R code):

```{r download}
fileUrl <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
download.file(fileUrl, destfile = paste0(getwd(), '/repdata%2Fdata%2Factivity.zip'))
unzip("repdata%2Fdata%2Factivity.zip",exdir = "activ")
data_activ<-read.csv(file = "activ/activity.csv")
```
## What is mean total number of steps taken per day?
Calculate the total number of steps taken per day
```{r sum}
steps<- tapply(data_activ$steps, data_activ$date, "sum", na.rm = TRUE)
```
Histogram and a barplot

Histogram
```{r hist}
hist(steps)
```

Barplot
```{r bar}
barplot(height = steps,space = 2)
```

Calculate the mean and median of the total number of steps taken per day
```{r mean_med}
mean(steps)
median(steps)
```

## What is the average daily activity pattern?

Time series plot of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
pl_Step<-tapply(data_activ$steps, data_activ$interval, "mean", na.rm = TRUE)
plot(names(pl_Step), pl_Step, type = "l",xlab="Interval", ylab="average number of steps taken, averaged across all days")
```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r max_1}
x<-max.col(t(pl_Step),"last")
pl_Step[x]
```

##Imputing missing values

Calculate the total number of missing values in the dataset
```{r}
sum(is.na(data_activ))
sum(is.na(data_activ$steps))
sum(is.na(data_activ$interval))
sum(is.na(data_activ$date))
```

Strategy for filling in all of the missing values in the dataset. Create a new dataset.
```{r}
na_mean<-mean(data_activ$steps, na.rm = TRUE)
data_activ[is.na(data_activ)]<-na_mean
```

Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day.
```{r}
steps_1<- tapply(data_activ$steps, data_activ$date, "sum", na.rm = TRUE)
hist(steps_1)
mean(steps_1)
median(steps_1)
mean(steps)
median(steps)
```
##Are there differences in activity patterns between weekdays and weekends?

Create a new factor variable in the dataset with two levels – “weekday” and “weekend” indicating whether a given date is a weekday or weekend day.
```{r}
Sys.setlocale("LC_TIME", "English")
data_activ['day'] <- weekdays(as.Date(data_activ$date))
data_activ$day[data_activ$day  %in% c('Saturday','Sunday') ] <- "weekend"
data_activ$day[data_activ$day  %in% c('Monday','Tuesday','Wednesday','Thursday','Friday') ] <- "weekday"
data_step <- aggregate(steps ~ interval + day, data_activ, mean)
```

Make a panel plot containing a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis). See the README file in the GitHub repository to see an example of what this plot should look like using simulated data.
```{r}
library(lattice)
xyplot(steps ~ interval | day, data_step,  type = "l", layout = c(1,2), xlab = "Interval (5 minutes)", ylab = "Average number of steps")
```

